Matching the Time of Emergence of Transboundary Fish Stocks to Lead Time for

### 2020-07-07 Scripts/Initial_Analysis.Rmd
Created new figures for 2005 year of proportion

# Run results
results <- PropChange(Taxon_List, links="y") %>% 
  mutate(per_mid_plot =ifelse(per_mid >= 50, 50,
                           ifelse(per_mid <= -50,-50,per_mid)
                           ),
         per_early_plot =ifelse(per_early >= 50, 50,
                           ifelse(per_early <= -50,-50,per_early)
                           )
         )

@@

x <- ggplot() +
  geom_sf(data = subset(World_map, sovereignt != "Antarctica"), size = 0.1, fill = "gray90", col = "gray90") +
  geom_sf(data = World_eez_sf, size = 0.1, fill = "white", col = "gray70") +
  geom_point(data = subset(Data, time_step == time & per_chng < 0),
             aes(start_lon,
                 start_lat,
                 col = per_chng),
             size = 0.05,
             col = "gray30",
             shape = 20,
             stroke = 1.5) +
  geom_path(data = subset(paths, time_step == time & per_chng > 0),
            aes(X, Y,
                group = interaction(line_id,subline_id),
                col = per_chng
            ),
            size = 0.3,
            arrow = arrow(length = unit(0.009, "npc"),
                          ends = "first"),
            show.legend = NA) +
  my_ggtheme_m() +
  scale_colour_viridis(
    name="Average Gain of\nStock-Share Ratio (%)",
    limits = c(0,max(Data$per_chng)),
    breaks = seq(0,max(Data$per_chng),5),
    # option="magma",
    direction = 1
  ) +
  ggsave("./Figures/figure_connections_early_n50.png",
         width = 10,
         height = 6,
         units = "in"
  )

@@

# Get taxon list
Taxon_List <- list.files(my_path("R",extra_path = "Emergence_yr"))

@@

Paths <- paste(my_path("R",extra_path = "Emergence_yr"),Taxon_List,"_emergence.txt",sep="")

@@

# Per Stock
stock_d_hist <- Eme_Res %>% 
  group_by(emerging_yr,taxon_key) %>%
  # summarise(n_tax = length(unique(eez_name))) %>%
  summarise(n()) %>% 
  mutate(
    level = "stock"
  ) %>% 
  select(1,3,4)
  # ggplot() +
  # geom_histogram(
  #   aes(
  #     x = emerging_yr
  #   ),
  #   stat = "count"
  # )

# Per EEZs
eez_d_hist <- Eme_Res %>% 
  group_by(eez_name,emerging_yr) %>% 
  # summarise(n_tax = length(unique(taxon_key))) %>% 
  summarise(n()) %>% 
  mutate(
    level = "EEZ"
  ) %>% 
  select(1,3,4)

hist_data <- stock_d_hist %>% 
  bind_rows(eez_d_hist)

ggplot() +
  geom_density(data = subset(hist_data, level == "EEZ"),
    aes(
      x = emerging_yr,
      fill = level
    ),
    stat = "count",
    alpha= 0.8,
    size=0.5,
  ) +
  geom_density(data = subset(hist_data, level == "stock"),
    aes(
      x = emerging_yr,
      fill = level
    ),
    stat = "count",
    alpha= 0.8,
    size=0.5,
  ) +
    scale_y_continuous("Frequency",
                       breaks = seq(0,90,10),
                       limits = c(0,100)
    ) +
    scale_x_continuous("Year of emergence",
                       breaks = seq(2000,2100,10)
    ) +
    my_ggtheme_p() +
    scale_fill_viridis(discrete = T)

@@

# Per Stock
stock_d <-  Eme_Res %>% 
  left_join(Neighbours) %>% 
    distinct(taxon_key,neighbour_id, .keep_all = TRUE) %>% 
    group_by(taxon_key) %>% 
    summarise(
      taxon_emer = min(emerging_yr)
    ) %>% 
    group_by(taxon_emer) %>% 
  summarise(
    n_tax = n()
  ) %>% 
  mutate(
    com_sum = cumsum(n_tax),
    level = "Stock"
  ) %>% 
    select(1,3,4)

  #  EEZ data
eez_d <-  Eme_Res %>% 
  left_join(Neighbours) %>% 
  filter(n_ens == 10) %>% 
    distinct(eez_name,neighbour_id, .keep_all = TRUE) %>% 
    group_by(eez_name) %>% 
    summarise(
      taxon_emer = min(emerging_yr)
    ) %>% 
    group_by(taxon_emer) %>% 
  summarise(
    n_tax = n()
  ) %>% 
  mutate(
    com_sum = cumsum(n_tax),
    level = "EEZ"
  ) %>% 
    select(1,3,4)

# Plot Data
plot_data <- stock_d %>% 
  bind_rows(eez_d)

  # filter(emerging_yr >= 2020) %>% 
  ggplot() +
    geom_area(data = subset(plot_data, level == "Stock"),
              aes(
                x = as.numeric(taxon_emer),
                y = com_sum,
                fill = level
              ),
              alpha= 0.8,
              size=0.5,
              colour="black"
    )  +
    geom_area(data = subset(plot_data, level == "EEZ"),
              aes(
                x = taxon_emer,
                y = com_sum,
                fill = level
              ),
              alpha= 0.8,
              size=0.5,
              colour="black"
    ) +
    # Comment out for option A (Change plot name!!)
    geom_hline(yintercept = length(unique(Eme_Res$eez_name)), color = "grey",linetype = "dashed") +
  geom_text(aes(label="Total number of EEZs", x = 2010, y = length(unique(Eme_Res$eez_name))+10), color = "grey70",size =3) +
    geom_hline(yintercept = length(unique(Eme_Res$taxon_key)), color = "grey",linetype = "dashed") +
  geom_text(aes(label="Total number of Taxa", x = 2010, y = length(unique(Eme_Res$taxon_key))+10), color = "grey70",size =3) +
    scale_y_continuous("Cumulatuve Curve",
                       breaks = seq(0,500,50),
                       limits = c(0,500)
    ) +
    scale_x_continuous("Year of emergence",
                       breaks = seq(2000,2100,10)
    ) +
    my_ggtheme_p() +
    scale_fill_viridis(discrete = T) +
  ggsave("./Figures/figure_accumulative_curve_B.png",
         width = 6,
         height = 6,
         units = "in"
  )
```

>>>>

# Run results
results <- PropChange(Taxon_List, links="y") %>% 
  filter(!is.na(eez_neighbour)) %>% 
  mutate(per_mid_plot =ifelse(per_mid >= 50, 50,
                           ifelse(per_mid <= -50,-50,per_mid)
                           ),
         per_early_plot =ifelse(per_early >= 50, 50,
                           ifelse(per_early <= -50,-50,per_early)
                           )
         )

# For dat availabillity
 # write_csv(results,
          # "proportion_change_2005.csv")

@@

x <- ggplot() +
  geom_sf(data = subset(World_map, sovereignt != "Antarctica"), size = 0.1, fill = "gray90", col = "gray90") +
  geom_sf(data = World_eez_sf, size = 0.1, fill = "white", col = "gray70") +
  geom_point(data = subset(Data, time_step == time & per_chng < 0),
             aes(start_lon,
                 start_lat,
                 col = per_chng),
             size = 0.05,
             col = "gray30",
             shape = 20,
             stroke = 1.5) +
  geom_path(data = subset(paths, time_step == time & per_chng > 0),
            aes(X, Y,
                group = interaction(line_id,subline_id),
                col = per_chng
            ),
            size = 0.3,
            arrow = arrow(length = unit(0.009, "npc"),
                          ends = "first"),
            show.legend = NA) +
  my_ggtheme_m() +
  scale_colour_viridis(
    name="Average Gain of\nStock-Share Ratio (%)",
    limits = c(0,max(Data$per_chng)),
    breaks = seq(0,max(Data$per_chng),5),
    # option="magma",
    direction = -1
  ) +
  ggsave("./Figures/figure_connections_early_n50.png",
         width = 10,
         height = 6,
         units = "in"
  )

##### Histogram of change

```{r hist_change}

 results %>% 
  gather("time_step","change",per_early,per_mid) %>% 
  filter(variable == "mean_eez" & 
           !is.na(change)
         ) %>%
ggplot() +
  geom_density(
               aes(
                 x = ifelse(change >= 100,100,change),
                 # x = change,
                 fill = ifelse(time_step == "per_early","q",time_step)
                 # fill = time_step,

               ),
               # stat = "count",
               # alpha= 0.8,
               size=0.1,
               # position = "stack"
  ) +
  scale_y_continuous("Density",
                     # breaks = seq(0,90,10),
                     # limits = c(0,100)
  ) +
  scale_x_continuous("Percentage Change",
                     breaks = seq(-75,500,25)
  ) +
  my_ggtheme_p() +
  theme(legend.position = "right") +
  scale_fill_viridis(discrete = T, 
                     option = "plasma",
                     alpha = 0.5,
                     name = "Time Step", labels = c("Middle", "Early")
                     ) +
  coord_flip() +
  ggsave("./Figures/hist_change.png",
         width = 6,
         height = 6,
         units = "in"
  )

@@

# Get taxon list
Taxon_List <- list.files(my_path("R",extra_path = "Emergence_2005"))

@@

Paths <- paste(my_path("R",extra_path = "Emergence_2005"),Taxon_List,"_emergence.txt",sep="")

@@

# Per Stock
stock_d_hist <- Eme_Res %>% 
  group_by(emerging_yr,taxon_key,Tresh) %>%
  # summarise(n_tax = length(unique(eez_name))) %>%
  summarise(n()) %>% 
  mutate(
    level = "stock"
  ) 
  # ggplot() +
  # geom_histogram(
  #   aes(
  #     x = emerging_yr
  #   ),
  #   stat = "count"
  # )

# Per EEZs
eez_d_hist <- Eme_Res %>% 
  group_by(eez_name,emerging_yr,Tresh) %>% 
  # summarise(n_tax = length(unique(taxon_key))) %>% 
  summarise(n()) %>% 
  mutate(
    level = "EEZ"
  ) %>% 
  ungroup() %>% 
  select(1,3,4)

hist_data <- stock_d_hist %>% 
  bind_rows(eez_d_hist) %>% 
  filter(Tresh != "NA")

ggplot() +
  geom_density(data = subset(hist_data, level == "EEZ"),
    aes(
      x = emerging_yr,
      fill = level
    ),
    stat = "count",
    alpha= 0.8,
    size=0.5,
  ) +
  geom_density(data = subset(hist_data, level == "stock"),
    aes(
      x = emerging_yr,
      fill = level
    ),
    stat = "count",
    alpha= 0.8,
    size=0.5,
  ) +
    scale_y_continuous("Frequency",
                       breaks = seq(0,90,10),
                       limits = c(0,100)
    ) +
    scale_x_continuous("Year of emergence",
                       breaks = seq(2000,2100,10)
    ) +
    my_ggtheme_p() +
    scale_fill_viridis(discrete = T) +
  facet_wrap(~Tresh)

@@

# Per Stock
stock_d <-  Eme_Res %>% 
  left_join(Neighbours) %>% 
    distinct(taxon_key,neighbour_id, .keep_all = TRUE) %>% 
    group_by(taxon_key,Tresh) %>% 
    summarise(
      taxon_emer = min(emerging_yr)
    ) %>% 
    group_by(taxon_emer,Tresh) %>% 
  summarise(
    n_tax = n()
  ) %>% 
  mutate(
    com_sum = cumsum(n_tax),
    level = "Stock"
  ) %>% 
    select(1,3,4)

  #  EEZ data
eez_d <-  Eme_Res %>% 
  left_join(Neighbours) %>% 
  filter(n_ens == 10) %>% 
    distinct(eez_name,neighbour_id, .keep_all = TRUE) %>% 
    group_by(eez_name,Tresh) %>% 
    summarise(
      taxon_emer = min(emerging_yr)
    ) %>% 
    group_by(taxon_emer,Tresh) %>% 
  summarise(
    n_tax = n()
  ) %>% 
  mutate(
    com_sum = cumsum(n_tax),
    level = "EEZ"
  ) %>% 
    select(1,3,4)

# Plot Data
plot_data <- stock_d %>% 
  bind_rows(eez_d) %>% 
  filter(Tresh != "NA")

  # filter(emerging_yr >= 2020) %>% 
  ggplot() +
    geom_area(data = subset(plot_data, level == "Stock"),
              aes(
                x = as.numeric(taxon_emer),
                y = com_sum,
                fill = level
              ),
              alpha= 0.8,
              size=0.5,
              colour="black"
    )  +
    geom_area(data = subset(plot_data, level == "EEZ"),
              aes(
                x = taxon_emer,
                y = com_sum,
                fill = level
              ),
              alpha= 0.8,
              size=0.5,
              colour="black"
    ) +
    # Comment out for option A (Change plot name!!)
    geom_hline(yintercept = length(unique(Eme_Res$eez_name)), color = "grey",linetype = "dashed") +
  geom_text(aes(label="Total number of EEZs", x = 2010, y = length(unique(Eme_Res$eez_name))+10), color = "grey70",size =3) +
    geom_hline(yintercept = length(unique(Eme_Res$taxon_key)), color = "grey",linetype = "dashed") +
  geom_text(aes(label="Total number of Taxa", x = 2010, y = length(unique(Eme_Res$taxon_key))+10), color = "grey70",size =3) +
    scale_y_continuous("Cumulatuve Curve",
                       breaks = seq(0,500,50),
                       limits = c(0,500)
    ) +
    scale_x_continuous("Year of emergence",
                       breaks = seq(2000,2100,10)
    ) +
    my_ggtheme_p() +
    scale_fill_viridis(discrete = T) +
    facet_wrap(~Tresh)
  # ggsave("./Figures/figure_accumulative_curve_B.png",
  #        width = 6,
  #        height = 6,
  #        units = "in"
  # )
```
